### 2021-04-02 control.tex

% Created by tikzDevice version 0.12.3 on 2021-03-27 20:28:52
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (722.70,361.35);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,361.35);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (361.35,361.35);
\end{scope}
\begin{scope}
\path[clip] ( 49.41, 39.63) rectangle (354.35,332.06);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 49.41, 39.63) rectangle (354.35,332.06);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 63.27, 52.92) --
	( 72.51, 59.52) --
	( 81.75, 66.11) --
	( 90.99, 72.69) --
	(100.23, 79.24) --
	(109.48, 85.78) --
	(118.72, 92.31) --
	(127.96, 98.81) --
	(137.20,105.30) --
	(146.44,111.78) --
	(155.68,118.24) --
	(164.92,124.68) --
	(174.16,131.11) --
	(183.40,137.52) --
	(192.64,143.92) --
	(201.88,150.30) --
	(211.12,156.67) --
	(220.36,163.02) --
	(229.60,169.35) --
	(238.84,175.67) --
	(248.08,181.98) --
	(257.32,188.27) --
	(266.56,194.54) --
	(275.81,200.80) --
	(285.05,207.04) --
	(294.29,213.27) --
	(303.53,219.49) --
	(312.77,225.69) --
	(322.01,231.88) --
	(331.25,238.05) --
	(340.49,244.20);
\definecolor{drawColor}{RGB}{230,159,0}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 63.27,205.70) --
	( 72.51,205.70) --
	( 81.75,205.70) --
	( 90.99,205.70) --
	(100.23,205.70) --
	(109.48,205.70) --
	(118.72,205.70) --
	(127.96,205.70) --
	(137.20,205.70) --
	(146.44,205.70) --
	(155.68,205.70) --
	(164.92,205.70) --
	(174.16,205.70) --
	(183.40,205.70) --
	(192.64,205.70) --
	(201.88,205.70) --
	(211.12,205.70) --
	(220.36,205.70) --
	(229.60,205.70) --
	(238.84,205.70) --
	(248.08,205.70) --
	(257.32,205.70) --
	(266.56,205.70) --
	(275.81,205.70) --
	(285.05,205.70) --
	(294.29,205.70) --
	(303.53,205.70) --
	(312.77,205.70) --
	(322.01,205.70) --
	(331.25,205.70) --
	(340.49,205.70);
\definecolor{drawColor}{RGB}{86,180,233}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 1pt off 3pt ,line join=round] ( 63.27, 87.55) --
	( 72.51, 95.59) --
	( 81.75,103.61) --
	( 90.99,111.61) --
	(100.23,119.58) --
	(109.48,127.53) --
	(118.72,135.45) --
	(127.96,143.35) --
	(137.20,151.22) --
	(146.44,159.07) --
	(155.68,166.90) --
	(164.92,174.71) --
	(174.16,182.49) --
	(183.40,190.25) --
	(192.64,197.99) --
	(201.88,205.70) --
	(211.12,213.39) --
	(220.36,221.06) --
	(229.60,228.71) --
	(238.84,236.33) --
	(248.08,243.93) --
	(257.32,251.51) --
	(266.56,259.07) --
	(275.81,266.61) --
	(285.05,274.12) --
	(294.29,281.62) --
	(303.53,289.09) --
	(312.77,296.54) --
	(322.01,303.97) --
	(331.25,311.38) --
	(340.49,318.77);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] ( 49.41, 39.63) rectangle (354.35,332.06);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.12] at ( 43.11,109.07) {1.50};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.12] at ( 43.11,190.12) {1.75};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.12] at ( 43.11,260.33) {2.00};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.12] at ( 43.11,322.26) {2.25};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.7pt,line join=round] ( 45.91,112.92) --
	( 49.41,112.92);

\path[draw=drawColor,line width= 0.7pt,line join=round] ( 45.91,193.98) --
	( 49.41,193.98);

\path[draw=drawColor,line width= 0.7pt,line join=round] ( 45.91,264.19) --
	( 49.41,264.19);

\path[draw=drawColor,line width= 0.7pt,line join=round] ( 45.91,326.12) --
	( 49.41,326.12);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.7pt,line join=round] ( 63.27, 36.13) --
	( 63.27, 39.63);

\path[draw=drawColor,line width= 0.7pt,line join=round] (132.58, 36.13) --
	(132.58, 39.63);

\path[draw=drawColor,line width= 0.7pt,line join=round] (201.88, 36.13) --
	(201.88, 39.63);

\path[draw=drawColor,line width= 0.7pt,line join=round] (271.18, 36.13) --
	(271.18, 39.63);

\path[draw=drawColor,line width= 0.7pt,line join=round] (340.49, 36.13) --
	(340.49, 39.63);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.12] at ( 63.27, 25.61) {0.6};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.12] at (132.58, 25.61) {0.8};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.12] at (201.88, 25.61) {1.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.12] at (271.18, 25.61) {1.2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.12] at (340.49, 25.61) {1.4};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (201.88, 10.06) {Generation interval ratio, $\bar{G}_{\mathrm{var}}/\bar{G}_{\mathrm{wt}}$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 16.64,185.84) {Strength};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 54.94,251.68) rectangle (226.84,324.71);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 61.94,293.37) rectangle ( 79.29,310.71);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{RGB}{86,180,233}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 1pt off 3pt ,line join=round] ( 63.68,302.04) -- ( 77.55,302.04);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{RGB}{86,180,233}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 1pt off 3pt ,line join=round] ( 63.68,302.04) -- ( 77.55,302.04);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{RGB}{86,180,233}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 1pt off 3pt ,line join=round] ( 63.68,302.04) -- ( 77.55,302.04);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 61.94,276.02) rectangle ( 79.29,293.37);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{RGB}{230,159,0}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 63.68,284.69) -- ( 77.55,284.69);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{RGB}{230,159,0}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 63.68,284.69) -- ( 77.55,284.69);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{RGB}{230,159,0}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 63.68,284.69) -- ( 77.55,284.69);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 61.94,258.68) rectangle ( 79.29,276.02);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 63.68,267.35) -- ( 77.55,267.35);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 63.68,267.35) -- ( 77.55,267.35);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 63.68,267.35) -- ( 77.55,267.35);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.12] at ( 86.29,298.18) {Constant speed intervention};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.12] at ( 86.29,280.84) {Constant strength intervention};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.12] at ( 86.29,263.49) {Epidemic};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.68] at ( 49.41,342.78) {A};
\end{scope}
\begin{scope}
\path[clip] (361.35,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round,fill=fillColor] (361.35,  0.00) rectangle (722.70,361.35);
\end{scope}
\begin{scope}
\path[clip] (416.36, 39.63) rectangle (715.70,332.06);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (416.36, 39.63) rectangle (715.70,332.06);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.1pt,line join=round] (429.97, 79.69) --
	(439.04, 79.69) --
	(448.11, 79.69) --
	(457.18, 79.69) --
	(466.25, 79.69) --
	(475.32, 79.69) --
	(484.39, 79.69) --
	(493.46, 79.69) --
	(502.53, 79.69) --
	(511.60, 79.69) --
	(520.68, 79.69) --
	(529.75, 79.69) --
	(538.82, 79.69) --
	(547.89, 79.69) --
	(556.96, 79.69) --
	(566.03, 79.69) --
	(575.10, 79.69) --
	(584.17, 79.69) --
	(593.24, 79.69) --
	(602.31, 79.69) --
	(611.38, 79.69) --
	(620.46, 79.69) --
	(629.53, 79.69) --
	(638.60, 79.69) --
	(647.67, 79.69) --
	(656.74, 79.69) --
	(665.81, 79.69) --
	(674.88, 79.69) --
	(683.95, 79.69) --
	(693.02, 79.69) --
	(702.09, 79.69);
\definecolor{drawColor}{RGB}{230,159,0}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] (429.97,318.77) --
	(439.04,298.97) --
	(448.11,280.79) --
	(457.18,264.03) --
	(466.25,248.54) --
	(475.32,234.18) --
	(484.39,220.82) --
	(493.46,208.37) --
	(502.53,196.74) --
	(511.60,185.84) --
	(520.68,175.62) --
	(529.75,166.00) --
	(538.82,156.95) --
	(547.89,148.40) --
	(556.96,140.32) --
	(566.03,132.67) --
	(575.10,125.42) --
	(584.17,118.54) --
	(593.24,112.00) --
	(602.31,105.77) --
	(611.38, 99.83) --
	(620.46, 94.17) --
	(629.53, 88.76) --
	(638.60, 83.59) --
	(647.67, 78.65) --
	(656.74, 73.91) --
	(665.81, 69.36) --
	(674.88, 65.00) --
	(683.95, 60.82) --
	(693.02, 56.79) --
	(702.09, 52.92);
\definecolor{drawColor}{RGB}{86,180,233}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 1pt off 3pt ,line join=round] (429.97,139.21) --
	(439.04,139.21) --
	(448.11,139.21) --
	(457.18,139.21) --
	(466.25,139.21) --
	(475.32,139.21) --
	(484.39,139.21) --
	(493.46,139.21) --
	(502.53,139.21) --
	(511.60,139.21) --
	(520.68,139.21) --
	(529.75,139.21) --
	(538.82,139.21) --
	(547.89,139.21) --
	(556.96,139.21) --
	(566.03,139.21) --
	(575.10,139.21) --
	(584.17,139.21) --
	(593.24,139.21) --
	(602.31,139.21) --
	(611.38,139.21) --
	(620.46,139.21) --
	(629.53,139.21) --
	(638.60,139.21) --
	(647.67,139.21) --
	(656.74,139.21) --
	(665.81,139.21) --
	(674.88,139.21) --
	(683.95,139.21) --
	(693.02,139.21) --
	(702.09,139.21);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] (416.36, 39.63) rectangle (715.70,332.06);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.12] at (410.06, 75.84) {0.100};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.12] at (410.06,139.36) {0.125};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.12] at (410.06,202.88) {0.150};

>>>>

% Created by tikzDevice version 0.12.3 on 2021-03-28 18:34:28
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (722.70,361.35);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.12] at ( 37.52, 56.08) {1.4};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.12] at ( 37.52,123.48) {1.6};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.12] at ( 37.52,182.94) {1.8};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.12] at ( 37.52,236.12) {2.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.12] at ( 37.52,284.23) {2.2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.12] at ( 37.52,328.15) {2.4};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.7pt,line join=round] ( 40.32, 59.94) --
	( 43.82, 59.94);

\path[draw=drawColor,line width= 0.7pt,line join=round] ( 40.32,127.34) --
	( 43.82,127.34);

\path[draw=drawColor,line width= 0.7pt,line join=round] ( 40.32,186.79) --
	( 43.82,186.79);

\path[draw=drawColor,line width= 0.7pt,line join=round] ( 40.32,239.98) --
	( 43.82,239.98);

\path[draw=drawColor,line width= 0.7pt,line join=round] ( 40.32,288.09) --
	( 43.82,288.09);

\path[draw=drawColor,line width= 0.7pt,line join=round] ( 40.32,332.01) --
	( 43.82,332.01);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 16.64,185.89) {Strength};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.12] at (404.47, 94.91) {0.100};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.12] at (404.47,167.50) {0.125};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.12] at (404.47,240.08) {0.150};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.12] at (404.47,312.67) {0.175};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.7pt,line join=round] (407.27, 98.77) --
	(410.77, 98.77);

\path[draw=drawColor,line width= 0.7pt,line join=round] (407.27,171.35) --
	(410.77,171.35);

\path[draw=drawColor,line width= 0.7pt,line join=round] (407.27,243.94) --
	(410.77,243.94);

\path[draw=drawColor,line width= 0.7pt,line join=round] (407.27,316.52) --
	(410.77,316.52);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (372.39,185.89) {Speed (1/days)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.68] at ( 43.82,342.78) {A};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.68] at (410.77,342.78) {B};
\end{scope}
\begin{scope}
\path[clip] ( 43.82, 39.69) rectangle (348.75,332.09);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 43.82, 39.69) rectangle (348.75,332.09);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 57.68, 52.98) --
	( 66.92, 57.30) --
	( 76.16, 61.73) --
	( 85.40, 66.27) --
	( 94.64, 70.93) --
	(103.89, 75.71) --
	(113.13, 80.60) --
	(122.37, 85.63) --
	(131.61, 90.78) --
	(140.85, 96.06) --
	(150.09,101.47) --
	(159.33,107.02) --
	(168.57,112.71) --
	(177.81,118.54) --
	(187.05,124.52) --
	(196.29,130.64) --
	(205.53,136.92) --
	(214.77,143.36) --
	(224.01,149.95) --
	(233.25,156.71) --
	(242.49,163.63) --
	(251.73,170.73) --
	(260.97,177.99) --
	(270.21,185.44) --
	(279.45,193.06) --
	(288.69,200.87) --
	(297.93,208.87) --
	(307.17,217.06) --
	(316.41,225.45) --
	(325.65,234.04) --
	(334.89,242.84);
\definecolor{drawColor}{RGB}{230,159,0}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 57.68,183.83) --
	( 66.92,183.83) --
	( 76.16,183.83) --
	( 85.40,183.83) --
	( 94.64,183.83) --
	(103.89,183.83) --
	(113.13,183.83) --
	(122.37,183.83) --
	(131.61,183.83) --
	(140.85,183.83) --
	(150.09,183.83) --
	(159.33,183.83) --
	(168.57,183.83) --
	(177.81,183.83) --
	(187.05,183.83) --
	(196.29,183.83) --
	(205.53,183.83) --
	(214.77,183.83) --
	(224.01,183.83) --
	(233.25,183.83) --
	(242.49,183.83) --
	(251.73,183.83) --
	(260.97,183.83) --
	(270.21,183.83) --
	(279.45,183.83) --
	(288.69,183.83) --
	(297.93,183.83) --
	(307.17,183.83) --
	(316.41,183.83) --
	(325.65,183.83) --
	(334.89,183.83);
\definecolor{drawColor}{RGB}{86,180,233}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 1pt off 3pt ,line join=round] ( 57.68, 89.66) --
	( 66.92, 94.92) --
	( 76.16,100.30) --
	( 85.40,105.82) --
	( 94.64,111.48) --
	(103.89,117.28) --
	(113.13,123.23) --
	(122.37,129.32) --
	(131.61,135.57) --
	(140.85,141.97) --
	(150.09,148.53) --
	(159.33,155.25) --
	(168.57,162.14) --
	(177.81,169.19) --
	(187.05,176.42) --
	(196.29,183.83) --
	(205.53,191.42) --
	(214.77,199.19) --
	(224.01,207.14) --
	(233.25,215.29) --
	(242.49,223.64) --
	(251.73,232.19) --
	(260.97,240.94) --
	(270.21,249.90) --
	(279.45,259.07) --
	(288.69,268.46) --
	(297.93,278.07) --
	(307.17,287.90) --
	(316.41,297.96) --
	(325.65,308.26) --
	(334.89,318.80);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] ( 43.82, 39.69) rectangle (348.75,332.09);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 48.06,251.71) rectangle (222.54,324.75);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 55.06,293.40) rectangle ( 72.41,310.75);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{RGB}{86,180,233}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 1pt off 3pt ,line join=round] ( 56.80,302.08) -- ( 70.67,302.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{RGB}{86,180,233}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 1pt off 3pt ,line join=round] ( 56.80,302.08) -- ( 70.67,302.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{RGB}{86,180,233}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 1pt off 3pt ,line join=round] ( 56.80,302.08) -- ( 70.67,302.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 55.06,276.06) rectangle ( 72.41,293.40);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{RGB}{230,159,0}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 56.80,284.73) -- ( 70.67,284.73);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{RGB}{230,159,0}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 56.80,284.73) -- ( 70.67,284.73);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{RGB}{230,159,0}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 56.80,284.73) -- ( 70.67,284.73);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 55.06,258.71) rectangle ( 72.41,276.06);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 56.80,267.39) -- ( 70.67,267.39);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 56.80,267.39) -- ( 70.67,267.39);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 56.80,267.39) -- ( 70.67,267.39);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.12] at ( 79.41,298.22) {Constant speed intervention};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.12] at ( 79.41,280.87) {Constant strength intervention};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.12] at ( 79.41,263.53) {Epidemic};
\end{scope}
\begin{scope}
\path[clip] (410.77, 39.69) rectangle (715.70,332.09);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (410.77, 39.69) rectangle (715.70,332.09);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.1pt,line join=round] (424.63, 98.77) --
	(433.87, 98.77) --
	(443.11, 98.77) --
	(452.35, 98.77) --
	(461.59, 98.77) --
	(470.83, 98.77) --
	(480.07, 98.77) --
	(489.31, 98.77) --
	(498.55, 98.77) --
	(507.79, 98.77) --
	(517.03, 98.77) --
	(526.28, 98.77) --
	(535.52, 98.77) --
	(544.76, 98.77) --
	(554.00, 98.77) --
	(563.24, 98.77) --
	(572.48, 98.77) --
	(581.72, 98.77) --
	(590.96, 98.77) --
	(600.20, 98.77) --
	(609.44, 98.77) --
	(618.68, 98.77) --
	(627.92, 98.77) --
	(637.16, 98.77) --
	(646.40, 98.77) --
	(655.64, 98.77) --
	(664.88, 98.77) --
	(674.12, 98.77) --
	(683.36, 98.77) --
	(692.60, 98.77) --
	(701.84, 98.77);
\definecolor{drawColor}{RGB}{230,159,0}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] (424.63,318.80) --
	(433.87,306.04) --
	(443.11,293.62) --
	(452.35,281.53) --
	(461.59,269.76) --
	(470.83,258.31) --
	(480.07,247.16) --
	(489.31,236.31) --
	(498.55,225.75) --
	(507.79,215.47) --
	(517.03,205.47) --
	(526.28,195.73) --
	(535.52,186.25) --
	(544.76,177.03) --
	(554.00,168.05) --
	(563.24,159.31) --
	(572.48,150.80) --
	(581.72,142.52) --
	(590.96,134.46) --
	(600.20,126.62) --
	(609.44,118.98) --
	(618.68,111.55) --
	(627.92,104.32) --
	(637.16, 97.28) --
	(646.40, 90.42) --
	(655.64, 83.75) --
	(664.88, 77.26) --
	(674.12, 70.94) --
	(683.36, 64.79) --
	(692.60, 58.81) --
	(701.84, 52.98);
\definecolor{drawColor}{RGB}{86,180,233}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 1pt off 3pt ,line join=round] (424.63,166.78) --
	(433.87,166.78) --
	(443.11,166.78) --
	(452.35,166.78) --
	(461.59,166.78) --
	(470.83,166.78) --
	(480.07,166.78) --
	(489.31,166.78) --
	(498.55,166.78) --
	(507.79,166.78) --
	(517.03,166.78) --
	(526.28,166.78) --
	(535.52,166.78) --
	(544.76,166.78) --
	(554.00,166.78) --
	(563.24,166.78) --
	(572.48,166.78) --
	(581.72,166.78) --
	(590.96,166.78) --
	(600.20,166.78) --
	(609.44,166.78) --
	(618.68,166.78) --
	(627.92,166.78) --
	(637.16,166.78) --
	(646.40,166.78) --
	(655.64,166.78) --
	(664.88,166.78) --
	(674.12,166.78) --
	(683.36,166.78) --
	(692.60,166.78) --
	(701.84,166.78);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] (410.77, 39.69) rectangle (715.70,332.09);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.7pt,line join=round] ( 59.39, 36.19) --
	( 59.39, 39.69);

\path[draw=drawColor,line width= 0.7pt,line join=round] (196.29, 36.19) --
	(196.29, 39.69);

\path[draw=drawColor,line width= 0.7pt,line join=round] (334.89, 36.19) --
	(334.89, 39.69);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,361.35);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.12] at ( 59.39, 25.68) {0.67};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.12] at (196.29, 25.68) {1.00};
